### 2021-06-04 README.Rmd
sfsfsfs

You will ideally soon be able to install this on CRAN, as follows:

@@

Until then, you can install the development version of this package through the `devtools` package.

@@

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_mids()`: adds Correlates of War (CoW) Militarized Interstate Dispute (MID) data to dyad-year data frame
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_gml_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data. (DEPRECATED)
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `add_ucdp_onsets()`: adds UCDP onsets to state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (CoW-MID, v. 5.0)
- `cow_mid_dirdisps`: Correlates of War Militarized Interstate Dispute data (directed dyadic dispute-year, v. 5.0) 
- `cow_mid_disps`: Correlates of War Militarized Interstate Dispute data (abbreviated dispute-level, v. 5.0) 
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gml_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (Gibler-Miller-Little, v. 2.1.1)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `maoz_powers`: Zeev Maoz' global/regional power data.
- `ucdp_acd`: a (not quite) dyad-year and (not quite) state-year data set on armed conflict episodes
- `ucdp_onsets`: a state-year data set of UCDP armed conflict onsets/episodes.

@@

tic()
create_dyadyears() %>%
  # Add GML MIDs 
  add_gml_mids(keep=NULL) %>%
  # Add Correlates of War MIDs 
  add_cow_mids(keep=NULL) %>%
  # add peace years
  add_peace_years() %>%
  # Add Gleditsch-Ward codes, because we can
  add_gwcode_to_cow() %>%
  # Add strategic rivalry data
  add_strategic_rivalries() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance. No default, must specify "cow" or "gw"
  add_minimum_distance(system = "cow") %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp(system = "cow") %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()

>>>>

You can install this on CRAN, as follows:

@@

You can install the development version of this package through the `devtools` package. The development version of the package invariably has more goodies, but may or may not be at various levels of stress-testing.

@@

- `add_archigos()`: adds some summary variables from Archigos about political leaders for state-year or dyad-year data.
- `add_atop_alliance()`: adds ATOP alliance information to dyad-year data.
- `add_capital_distance()`: adds capital-to-capital distance (in kilometers, "as the crow flies") to dyad-year or state-year data.
- `add_ccode_to_gw()`: 	Add Correlates of War state system codes to dyad-year or state-year data with Gleditsch-Ward state codes.
- `add_contiguity()`: adds Correlates of War direct contiguity data to dyad-year or state-year data.
- `add_cow_alliance()`: adds Correlates of War major alliance information to dyad-year data.
- `add_cow_majors()`: adds Correlates of War major power information to dyad-year or state-year data.
- `add_cow_mids()`: adds Correlates of War (CoW) Militarized Interstate Dispute (MID) data to dyad-year data frame
- `add_cow_trade()`: adds Correlates of War trade data to dyad-year or state-year data.
- `add_democracy()`: adds estimates of democracy/levels of democracy to dyad-year or state-year data.
- `add_gwcode_to_cow():` adds Gleditsch-Ward state codes to dyad-year or state-year data with Correlates of War state codes.
- `add_gml_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data.
- `add_igos()`: adds Correlates of War International Governmental Organizations (IGOs) data to dyad-year or state-year data.
- `add_mids():` adds dyad-year information about ongoing MIDs and MID onsets from the Gibler-Miller-Little data. (DEPRECATED)
- `add_minimum_distance()`: adds minimum distance (in kilometers) to dyad-year or state-year data.
- `add_nmc()`: adds estimates of national material capabilities (from Correlates of War) to dyad-year or state-year data.
- `add_peace_years()`: Add Peace Years to Your Conflict Data
- `add_sdp_gdp()`: adds estimates of (gross and surplus) domestic product and population size to dyad-year or state-year data
- `add_strategic_rivalries()`: Add Thompson and Dreyer's (2012) strategic rivalry data to dyad-year data frame
- `add_ucdp_acd()`: Add UCDP Armed Conflict Data to state-year data frame
- `add_ucdp_onsets()`: adds UCDP onsets to state-year data
- `create_dyadyears()`: converts Correlates of War or Gleditsch-Ward state system membership data into dyad-year format
- `create_statedays()`: converts Correlates of War or Gleditsch-Ward state membership data into state-day format..
- `create_stateyears()`: converts Correlates of War or Gleditsch-Ward state membership data into state-year format.
- `filter_prd()`: filters dyad-year data frame to just "politically relevant" dyads.

@@

- `archigos`: an abbreviated version of the Archigos data, used internally
- `atop_alliance:` directed dyad-year alliance data from ATOP
- `capitals`: a list of capitals and capital transitions for Correlates of War state system members
- `ccode_democracy`: Correlates of War state-year data with three different estimates of democracy (Varieties of Democracy, Polity, Xavier Marquez/Pemstein et al.'s "(Quick) Unified Democracy Scores").
- `cow_alliance`: directed dyad-year alliance formation data from the Correlates of War
- `cow_contdir`: Correlates of War Direct Contiguity Data (v. 3.2)
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_gw_years`: a yearly data frame including information about Correlates of War and Gleditsch-Ward states.
- `cow_igo_ndy`: non-directed dyad-year data for Correlates of War intergovernmental organizations data.
- `cow_igo_sy`: state-year data for Correlates of War intergovernmental organizations data.
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (CoW-MID, v. 5.0)
- `cow_mid_dirdisps`: Correlates of War Militarized Interstate Dispute data (directed dyadic dispute-year, v. 5.0) 
- `cow_mid_disps`: Correlates of War Militarized Interstate Dispute data (abbreviated dispute-level, v. 5.0) 
- `cow_mindist`: the minimum distance between Correlates of War states, in kilometers, in non-directed dyad-year format (1946-2015)
- `cow_nmc`: Correlates of War National Material Capabilities data (version 5.0)
- `cow_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `cow_trade_sy`: Correlates of War state-year trade data (version 4.0)
- `creg`: Composition of Religious and Ethnic Groups (CREG) Fractionalization/Polarization Estimates
- `gml_dirdisp`: directed dispute-year data from version 2.1.1 of the Gibler-Miller-Little inter-state dispute data.
- `gml_mid_ddydisps`:  Directed Dyadic Dispute-Year Data with No Duplicate Dyad-Years (Gibler-Miller-Little, v. 2.1.1)
- `gw_ddy`: a full directed dyad-year data frame of Gleditsch-Ward state system members
- `gw_mindist`: the minimum distance between  Gleditsch-Ward states, in kilometers, in non-directed dyad-year format (1946-2015)
- `gw_sdp_gdp`: (Surplus and Gross) Domestic Product for Correlates of War States
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
- `hief`: Historical Index of Ethnic Fractionalization data
- `maoz_powers`: Zeev Maoz' global/regional power data
- `rugged`: Rugged/Mountainous Terrain Data
- `td_rivalries`: Thompson and Dreyer's (2012) Strategic Rivalries, 1494-2010
- `ucdp_acd`: a (not quite) dyad-year and (not quite) state-year data set on armed conflict episodes
- `ucdp_onsets`: a state-year data set of UCDP armed conflict onsets/episodes.

@@

tic()
create_dyadyears() %>%
  # Add GML MIDs 
  add_gml_mids(keep=NULL) %>%
  # Add Correlates of War MIDs 
  add_cow_mids(keep=NULL) %>%
  # add peace years
  add_peace_years() %>%
  # Add Gleditsch-Ward codes, because we can
  add_gwcode_to_cow() %>%
  # Add strategic rivalry data
  add_strategic_rivalries() %>%
  # Add trade data
  add_cow_trade() %>%
  # Add capital-to-capital distance
  add_capital_distance() %>%
  # Add contiguity information
  add_contiguity() %>%
  # Add major power data
  add_cow_majors() %>%
  # Add democracy variables
  add_democracy() %>%
  # Add IGOs data
  add_igos() %>%
  # Add National Material Capabilities
  add_nmc() %>%
  # add alliance data from Correlates of War
  add_cow_alliance() %>%
  # add alliance data from ATOP
  add_atop_alliance() %>%
  # add minimum distance. No default, must specify "cow" or "gw"
  add_minimum_distance(system = "cow") %>%
  # add Archigos data
  add_archigos() %>%
  # add gross and surplus GDP data
  add_sdp_gdp(system = "cow") %>%
  # add terrain ruggedness data, if you wanted it
  add_rugged_terrain() %>%
  # you should probably filter to politically relevant dyads earlier than later...
  # Or not, it's your time and computer processor...
  filter_prd()
toc()
